Enriching Object Detection with 2D-3D Registration and Continuous Viewpoint

### 2014-11-14 experiments.tex
started another pass over 6

%
In this section, we give an experimental evaluation of our approach,
highlighting two different aspects.

First, we demonstrate that our method can be used for multi-view
object class detection in isolation. It can be applied in a sliding
window fashion and deliver 2D bounding box as well as viewpoint
information. Our method compares on par to state-of-the-art in this
case (Sect.~\ref{sec:exp_iso}).

Second, we show that our method can be used to complement the
detections provided by an existing object class detector, such
as DPM~\cite{Felzenszwalb10} or RCNN~\cite{Girshick14}. In this case,
we show a considerable performance improvement compared to previous
work in the task of joint object class detection and viewpoint
estimation (Sect.~\ref{sec:exp_enrich}).

@@

\subsection{Variations of WHO}
\label{sec:variations}
To validate our approach, we run an ensemble of NZ-WHO templates as a bank of exemplar detectors and compare its performance with other WHO variants. Since WHO variants uses HOG features, they are slower than HOG templates but WHO variants in general performs better than WHO by significant margin. However, WHO using Cholesky decomposition with Gaussian Elemination takes the most time yet performs worse than NZ-WHO which is two order of magnitude faster to generate.

@@

\begin{table*}[!htbp]
    \footnotesize
    \begin{center}
\begin{tabular}{|c|c|r|c|r|}
\hline
Methods (AP/MPPE) & before calibration  & time & after calibration \cite{Aubry14} & time \\
\hline\hline
HOG\cite{Dalal05}     & 72.3 / 65.0           &  31ms  & 60.4 / 50.2                 & 8.7 sec \\ 
WHO\cite{Hariharan12} & 82.1 / 85.4           &  3811ms& 84.4 / 83.0                 & 12.4 sec  \\
WHO-CG                & 81.7 / \textbf{84.9}  &  104ms & 83.7 / 87.3                 & 8.3 sec \\
WHO-CG-Z              & 54.4 / 65.1           &  103ms & \textbf{92.8} / 86.7        & 8.7 sec  \\
% NZC-WHO-Z    & 89.10/\textbf{78.64} &    & 91.15/74.79                  &     \\
NZ-WHO-CG             & \textbf{90.0} / 82.8  &   79ms & 90.3 / \textbf{86.8}        & 8.5 sec   \\
\hline
\end{tabular}
\end{center}
\caption{Average Precision(AP) and Mean Precision in Pose Estimation (MPPE) \cite{Lopez-Sastre11} variations of WHO on 3DObject Car dataset\cite{Savarese07}. WHO refers to standard WHO using the method presented in \cite{Hariharan12}, WHO-CG uses iterative Conjugate Gradient method to generate WHO. WHO-CG-Z uses whiten the whole template and zero out textureless region. NZ-WHO-CG is the NZ-WHO which whitens only non-zero cells using iterative Conjugate Gradient method. The time column indicates the time to generate one template. We followed calibration procedure presented in \cite{Aubry14}.}
\label{tab:who_initializations}
\end{table*}

>>>>

%
In this section, we give an experimental evaluation of our approach,
highlighting three different aspects.

First, we verify that our NZ-WHO method delivers performance that is
at least on par with the original WHO formulation~\cite{Hariharan12} in terms of
accuracy, while at the same time resulting in large computational
savings (Sect.~\ref{sec:variations}).

Second, we demonstrate that our method can be used for multi-view
object class detection in isolation. It can be applied in a sliding
window fashion and deliver 2D bounding box as well as viewpoint
information. Our method compares on par to state-of-the-art in this
case (Sect.~\ref{sec:exp_iso}).

And third, we show that our method can be used to complement the
detections provided by an existing object class detector, such
as DPM~\cite{Felzenszwalb10} or RCNN~\cite{Girshick14}. In this case,
we show a considerable performance improvement compared to previous
work in the task of joint object class detection and viewpoint
estimation (Sect.~\ref{sec:exp_enrich}).

@@

\subsection{WHO Variants}
\label{sec:variations}
To validate our approach, we run an ensemble of NZ-WHO templates as a bank of exemplar detectors and compare its performance with other WHO variants. Since WHO variants uses HOG features, they are slower than HOG templates but WHO variants in general performs better than WHO by significant margin. However, WHO using Cholesky decomposition with Gaussian Elemination takes the most time yet performs worse than NZ-WHO which is two order of magnitude faster to generate.

@@

\begin{table}[!htbp]
    \footnotesize
    \setlength{\tabcolsep}{1pt}
    \centering
\begin{tabular}{|c|c|r|c|r|}
\hline
Methods (AP/MPPE) & before calib.  & time & after calib.~\cite{Aubry14} & time \\
\hline\hline
HOG\cite{Dalal05}     & 72.3 / 65.0           &  31ms  & 60.4 / 50.2                 & 8.7 sec \\ 
WHO\cite{Hariharan12} & 82.1 / 85.4           &  3811ms& 84.4 / 83.0                 & 12.4 sec  \\
WHO-CG                & 81.7 / \textbf{84.9}  &  104ms & 83.7 / 87.3                 & 8.3 sec \\
WHO-CG-Z              & 54.4 / 65.1           &  103ms & \textbf{92.8} / 86.7        & 8.7 sec  \\
% NZC-WHO-Z    & 89.10/\textbf{78.64} &    & 91.15/74.79                  &     \\
NZ-WHO-CG             & \textbf{90.0} / 82.8  &   79ms & 90.3 / \textbf{86.8}        & 8.5 sec   \\
\hline
\end{tabular}
\caption{Average Precision(AP) and Mean Precision in Pose Estimation (MPPE) \cite{Lopez-Sastre11} variations of WHO on 3DObject Car dataset\cite{Savarese07}. WHO refers to standard WHO using the method presented in \cite{Hariharan12}, WHO-CG uses iterative Conjugate Gradient method to generate WHO. WHO-CG-Z uses whiten the whole template and zero out textureless region. NZ-WHO-CG is the NZ-WHO which whitens only non-zero cells using iterative Conjugate Gradient method. The time column indicates the time to generate one template. We followed calibration procedure presented in \cite{Aubry14}.}
\label{tab:who_initializations}
\end{table}
